Effect of net size on estimates of abundance, size, age and sex ratio of *Mysis

### 2016-01-12 _drafts/2016-01-12-Appendix.Rmd
updated params.json

---
title: Effect of net size on estimates of abundance, size, age and sex ratio of Mysis
  diluviana Journal of Great Lakes Research - Statistical Analysis Appendix
author: "John Tipton"
date: "January 12, 2016"
layout: post
---

>>>>

---
title: Effect of net size on estimates of abundance, size, age and sex ratio of *Mysis
  diluviana* - Statistical Analysis Appendix
author: "John Tipton"
date: "January 12, 2016"
layout: post
---
